Cost-Benefit Analysis

### 2023-05-29 workflow/notebooks/cost-benefit-analysis.Rmd
Just plot decision threshold

@@

- Vince: consider bezlotoxumab since it targets the toxin, mouse models show it reduces organ damage.
- Krishna: bezlotoxumab clinical trials didn't find signal for limiting severity. however fidaxomicin is superior to vancomycin for cure and time to resolution of diarrhea ([IDSA 2021 update](https://doi.org/10.1093/cid/ciab549)).

>>>>

### [decision curve analysis](https://journals.sagepub.com/doi/10.1177/0272989X06295361)

QALYs are prone to systemic biases. 
We can sidestep using them by doing decision curve analysis instead.
Weight the relative harms of FP and FN results.

- incidence of severe CDI
- net benefit = $\frac{TP}{n} - \frac{FP}{n} \times \frac{p_t}{1-p_t}$ (Peirce 1884)
- plot net benefit vs probability threshold ($p_t$).
- harm of treating with fidaxomicin instead of vancomycin: more expensive. by how much?
- assume all patients severe vs no patients severe.

```{r decision-curve}
library(here)
library(tidyverse)
thresh_dat <- read_csv(here('results','thresholds_results_aggregated.csv'))
thresh_dat %>% 
  filter(dataset == 'int',outcome=='attrib',seed==100) %>% 
  ggplot(aes(decision_threshold, net_benefit, 
             color = strategy, linetype = strategy)) +
  geom_line(alpha = 0.6) +
  theme_sovacool()
```

@@

- Vince: consider bezlotoxumab since it targets the toxin, mouse models show it reduces organ damage.
- Krishna: bezlotoxumab clinical trials didn't find signal for limiting severity. however fidaxomicin is superior to vancomycin for cure and time to resolution of diarrhea ([IDSA 2021 update](https://doi.org/10.1093/cid/ciab549)).
  - Fidaxomicin [NNT=10](https://thennt.com/nnt/oral-fidaxomicin-versus-vancomycin-clostridioides-difficile-infection/) for global cure (no recurrence occured).

NNT for Fidaxomicin, FMT, and/or Bezlotoxumab. Current standard is Vancomycin
because it's cheaper than Fidaxomicin, even though IDSA recommends Fidaxomicin.

rough estimate of costs.
current: everyone gets vancomycin.
potential: patients flagged as severe get fidaxomicin. based on NNB, estimate
how much money saved in averting severe outcomes.
